---
title: "R Notebook"
output: html_notebook
---

Data, Clustering Results and Visualization Functions From Duo et al (2018)

 Bioconductor version: Release (3.11)

Preprocessed experimental and simulated scRNA-seq data sets used for evaluation of clustering methods for scRNA-seq data in Duo et al (2018). Also contains results from applying several clustering methods to each of the data sets, and functions for plotting method performance.

Author: Angelo Duo, Charlotte Soneson 

## Installation

We use dataset from package DuoClustering2018:
```{r}
# if (!requireNamespace("BiocManager", quietly = TRUE))
#     install.packages("BiocManager")
# BiocManager::install("DuoClustering2018")

```

Another package *SingleCellExperiment** is required in the following steps.
ref: https://bioconductor.org/packages/release/bioc/html/SingleCellExperiment.html
```{r}
# BiocManager::install("SingleCellExperiment")
# BiocManager::install("SC3")
# BiocManager::install("scater")
# BiocManager::install("scran")
# BiocManager::install("Rtsne")
```

